Stabilization-Free Virtual Element Methods

### 2023-02-04 reports/response.tex

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggest. We have revised it.

\medskip

\item \textsf{Line 323; the operator $I_K^{\div}$ should be defined explicitly.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
The definition of the $L^2$-bounded commuting projection operator is not trivial, and can not be explicitly given shortly.
Reference \cite{ChristiansenWinther2008} constructs such an operator in the whole paper. 
And references \cite{ArnoldGuzman2021,FalkWinther2014} focus on the construction of local $L^2$-bounded commuting projection operators in the whole paper. Thus in the revised manuscript, we present the properties of $I_K^{\div}$ instead of the explicit definition. And we use the local $L^2$-bounded operator in \cite{ArnoldGuzman2021,FalkWinther2014} instead of that in \cite{ChristiansenWinther2008}.

The modification is given as follows.

Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
\begin{equation}\label{eq:20230203}  
\|I_K^{\div}\boldsymbol{\psi}\|_{0,K} \lesssim \|\boldsymbol{\psi}\|_{0,K}\quad\forall~\boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K),
\end{equation}
\[
\div(I_K^{\div}\boldsymbol{\psi})=\div\boldsymbol{\psi} \quad \textrm{ for } \boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K) \textrm{ satisfying } \div\boldsymbol{\psi}\in V_{k-2}^{L^2}(K),
\]
where $
V_{k-2}^{L^2}(K)=\{v\in L^2(K): v|_{T}\in \mathbb P_{k-2}(T) \textrm{ for } T\in\mathcal T_K\}
$.

@@

\medskip

\item \textsf{Eq. (3.28); can you elaborate more on the first inequality? Moreover, the second inequality follows from the bound on line 322; you should underline this.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have revised them as follows.

% We have
% \begin{equation*}%\label{eq:20220324-6}
% \div\boldsymbol{\phi}_2=-\div(I_K^{\div}(\nabla w))=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1).
% \end{equation*}
It follows from \eqref{eq:20230203} and (3.29) (i.e. the bound on line 322) that
\begin{equation*}%\label{eq:20220324-7}
\|\boldsymbol{\phi}_2\|_{0,K}=\|I_K^{\div}(\nabla w)\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation*}

@@

\medskip

\item \textsf{After line 336, can you state the difference between the space defined on line 336 and that on line 263?.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have compared space $\boldsymbol{V}_{k-1}^{\rm div}(K)$ and space $\mathbb{V}_{k-1}^{\rm div}(K)$ in question 7.
Indeed, on each face $F\in\mathcal F(K)$, $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ but $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ is a piecewise polynomial for $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$.

@@

\medskip

\item \textsf{The definition of the DoFs in eqs. (4.3) and (4.4) is wrong: you should first pick bases of bulk and face polynomial spaces and define the moments accordingly.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have revised DoFs (4.3) and (4.4) as
\begin{align*}
\frac{1}{|F|}(v, \phi_i^F)_F, & \quad i=1,\ldots, \dim\mathbb P_{k-1}(F), F\in\mathcal F(K), 
\\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K),
\end{align*}
where $\{\phi_i^F\}_{i=1}^{\dim\mathbb P_{k-1}(F)}$ is a basis of $\mathbb P_{k-1}(F)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.

@@

\medskip

\item \textsf{Line 381; the space $\mathbb P_p\backslash\mathbb P_{p-2}$ is not defined as an orthogonal complement, but rather as any completion of the smaller space into the larger one. The two definitions are equivalent if you use orthogonal polynomial bases, which I humbly think is not what you are actually doing.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Now we use $\mathbb P_{k-2}^{\perp}(K)$ to denote the orthogonal complement space of $\mathbb P_{k-2}(K)$ in $\mathbb P_{k}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.

@@

\medskip

\item \textsf{You may wish to shorten up or even remove the proof of Lemma 4.1, which is standard in the virtual element literature.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
One reviewer has questions on the proof of Lemma 4.1. Thus we modify the proof and keep it.

@@

\medskip

\item \textsf{Line 406; “inequality”$-\!\!\!-\!\!\!>$“inequalities”; moreover, mention that you use both $H^1$-$L^2$ and $L^2$ boundary-$L^2$ bulk inverse inequalities.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
They have been corrected.

@@

\medskip

\item \textsf{Line 408; is [11, (2.15)] the proper reference for the Poincar\'e-Friedrichs inequality? I think it is a standard result and you may wish to cite any standard PDE book.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have changed it to reference \cite{Necas1967}.

@@

\medskip

\item \textsf{Eq. (4.12); if you complete the sequence of identities and inequalities with $h_k^2|v|_{1,K}^2$, you get indeed a norm equivalence (and not only an upper bound).}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have the norm equivalence
\[
\|v\|_{0,K}^2\eqsim \|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_F\|Q_{k-1}^Fv\|_{0,F}^2 \quad\forall~v\in V_k(K),
\]
and the inequality
\[
h_K|v|_{1,K}\lesssim \|v\|_{0,K}\quad\forall~v\in V_k(K).
\]
But we do not have 
the equivalence
\[
h_K|v|_{1,K}\eqsim \|v\|_{0,K}\quad\forall~v\in V_k(K).
\]
Indeed, when $v$ is a nonzero constant, we have
$$
h_K|v|_{1,K}=0,\quad \|v\|_{0,K}>0.
$$

@@

\medskip

\item \textsf{Lines 445 and 456; explain from where the term $Q_0^K(\div\phi)$ appears.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Since $v\in L_0^2(K)$, then $Q_{0}^Kv=0$ and $v=v-Q_{0}^Kv$. Noting that $Q_{0}^K(\div\boldsymbol{\phi})$ is constant, we have
$$
(Q_{0}^K(\div\boldsymbol{\phi}), v)_K=(Q_{0}^K(\div\boldsymbol{\phi}), v-Q_{0}^Kv)_K=0.
$$

@@

\medskip

\item \textsf{Provide more details on the inequality on lines 457-458.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Notice that $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$.
We get from 
\begin{align*}
\|\boldsymbol{\phi}\|_{0,K}%&\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \\
&\lesssim h_K\|\div\boldsymbol{\phi}-Q_0^K(\div\boldsymbol{\phi})\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}
\end{align*}
that
\[
\|\boldsymbol{\phi}\|_{0,K}\lesssim h_K^{-1}\|Q_{k-2}^Kv\|_{0,K} +\sum_{F\in\mathcal F(K)}h_F^{-1/2}\|Q_{k-1}^Fv\|_{0,F}.
\]

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
It has been corrected.

\medskip

\item \textsf{The definition of the DoFs in eqs. (5.1), (5.2), and (5.3) is wrong: you should first pick bases of bulk and face polynomial spaces and define the moments accordingly.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We have revised DoFs (5.1), (5.2), and (5.3) as
\begin{align*}
v(\delta), & \quad \delta\in\mathcal V(K), \\
\frac{1}{|e|}(v, \phi_i^e)_e, & \quad i=1,\ldots, k-1, e\in\mathcal E(K), \\
\frac{1}{|K|}(v, \phi_i^K)_K, & \quad i=1,\ldots, \dim\mathbb P_{k-2}(K),
\end{align*}
where $\{\phi_i^e\}_{i=1}^{k-1}$ is a basis of $\mathbb P_{k-2}(e)$, and $\{\phi_i^K\}_{i=1}^{\dim\mathbb P_{k-2}(K)}$ a basis of $\mathbb P_{k-2}(K)$.

@@

\medskip

\item \textsf{You may wish to reduce or even drop the proof of Theorem 5.3, which appears to be a standard Strang-type result for the VEM.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have removed the proof of Theorem 5.3.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{Minor issues (I will not highlight all the typos but only few of them as an example):
\begin{itemize}
\item line 3; “Poisson”$-\!\!\!-\!\!\!>$“the Poisson”;
\item line 24; “space”$-\!\!\!-\!\!\!>$“the space”;
\item line 31; “space”$-\!\!\!-\!\!\!>$“that the space”;
\item line 43; “usual”$-\!\!\!-\!\!\!>$“the usual”;
\item line 49; “space”$-\!\!\!-\!\!\!>$“the space”;
\item line 68; “. And”$-\!\!\!-\!\!\!>$“and”;
\item line 81; “banach”$-\!\!\!-\!\!\!>$“Banach”;
\item line 82; “and $\mathbb K$, where $\mathbb K$”$-\!\!\!-\!\!\!>$“and $\mathbb K$”; 
\item line 105; “surface”$-\!\!\!-\!\!\!>$“the surface”;
\item line 107; “smooth”$-\!\!\!-\!\!\!>$“a smooth”;
\item line 262; “shape”$-\!\!\!-\!\!\!>$“the shape”;
\item line 347; “discrete”$-\!\!\!-\!\!\!>$“the discrete”;
\item lines 465-466; “DoF”$-\!\!\!-\!\!\!>$“DoFs”; “is”$-\!\!\!-\!\!\!>$“are”; “vanishes”$-\!\!\!-\!\!\!>$“vanish”; 
\item line 511; “inequlities”$-\!\!\!-\!\!\!>$“inequalities”;
\item line 549; “DoFs”$-\!\!\!-\!\!\!>$“the DoFs”.
\end{itemize}
}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We proofread the paper carefully. All of them have been corrected.

@@

For the second question, it can be explained as follows:
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$

\medskip

\item \textsf{In the proof of Lemma 4.1, the authors claim that
$$
h_K^{\frac{1}{2}}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
$$
This is a sort of discrete trace inequality and the authors justify it by citing (A.3)-(A.4) in [15]. However, it is not apparent to me how this follows from (A.3)-(A.4). Moreover, the authors conclude that “with the multiplicative trace inequality”
$$
h_K^{\frac{1}{2}}\|v\|_{0,\partial K}\lesssim h_K^{-1}\|v\|_{0,K}.
$$
Again, this is a discrete trace inequality, and it is not specified why it is valid on the virtual space $V_k(K)$. The same goes for the arguments used in the proof of Lemma 4.3.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
\begin{itemize}
    \item 
For virtual function $v\in V_k(K)$, apply (A.3) in \cite{ChenHuang2020ncvem} to get
\[
h_K\|\Delta v\|_{0,K}\lesssim |v|_{1,K}.
\]
By (A.4) with $m=j=1$ in \cite{ChenHuang2020ncvem}, it follows that
\[
h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}+h_K\|\Delta v\|_{0,K}.
\]
Combining the last two inequalities yields
\[
h_K\|\Delta v\|_{0,K}+h_K^{1/2}\|\partial_nv\|_{0,\partial K}\lesssim |v|_{1,K}.
\]
\item The multiplicative trace inequality is
\[
\|v\|_{0,\partial K}\lesssim h_K^{-1/2}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \quad\forall~v\in H^1(K).
\]
Since $v\in V_k(K)\subset H^1(K)$, inserting the last multiplicative trace inequality into the inequality
\[
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,\partial K},
\]
we get
\begin{align*}
|v|_{1,K}&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1}\|v\|_{0,K}^{1/2}(\|v\|_{0,K}^{1/2}+h_K^{1/2}|v|_{1,K}^{1/2}) \\
&\lesssim h_K^{-1}\|v\|_{0,K}+h_K^{-1/2}\|v\|_{0,K}^{1/2}|v|_{1,K}^{1/2}.
\end{align*}
Then apply the Young's inequality to acquire
\[
|v|_{1,K}\lesssim h_K^{-1}\|v\|_{0,K}.
\]
\end{itemize}

### 2023-02-04 stabfreevem_sinum.tex
answer the first reviewer

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}. 
\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
the analysis is rather elaborate. 
\XH{
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
}

The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
\XH{The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}. And a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. Denote by $L_0^2(K)$ the space of all functions in $L^2(K)$ with zero integral.
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$, where $\mathbb{K}$ is the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

@@

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On face $F\in\mathcal F_h$, define surface divergence
\[
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
\]
For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.

@@

@@

@@

>>>>

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}. 
\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.
The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
the analysis is rather elaborate. 
\XH{
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
}

The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
\XH{The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto the space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

@@

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A stabilization-free nonconforming virtual element method in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming virtual element method in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. Denote by $L_0^2(K)$ the space of all functions in $L^2(K)$ with zero integral.
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a Banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$ being the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

@@

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On the face $F\in\mathcal F_h$, define surface divergence
\[
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
\]
For a smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.

@@

\begin{equation}\label{eq:202302031}  
\XH{Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the local $L^2$-bounded commuting projection operator in \cite{ArnoldGuzman2021,FalkWinther2014}, then
\begin{equation}\label{eq:20230203}  
\|I_K^{\div}\boldsymbol{\psi}\|_{0,K} \lesssim \|\boldsymbol{\psi}\|_{0,K}\quad\forall~\boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K),

@@

\div(I_K^{\div}\boldsymbol{\psi})=\div\boldsymbol{\psi} \quad \textrm{ for } \boldsymbol{\psi}\in \boldsymbol{H}_0(\div,K) \textrm{ satisfying } \div\boldsymbol{\psi}\in V_{k-2}^{L^2}(K).

@@

It follows from \eqref{eq:20230203} and \eqref{eq:202302031} that
